Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-09-19 paper/letter.tex
and
equivalente->equivalent

Are these values atypical? If \tol\ followed the fundamental
plane relationship between its mean surface brightness
$I_e$, the projected half-light radius $R_e$ and the velocity dispersion
$\sigma$, described by $\log I_e=1.6 \log\sigma - 1.21\log R_e +
0.55$ \cite{2009ApJ...698.1590G},  the expected velocity dispersion
should be on the order of $5 \pm 1$ 
\kms, which is a factor of $\sim$ $12$ - $60$ lower than the 
results from the multiphase-rotation models, respectively. 
These are equivalente to factors of $\sim$ $140$ - $3600$ on the
dynamical mass;
\tol\ seems to be significantly more massive than the expectation from
scaling relationships for dwarf ellipticals.
A factor of $100$ in dynamical mass could be accounted by dark matter if
\tol\ was hosted by a dark matter halo of  $\sim 10^{16}$ M$_{\odot}$
\cite{2011ApJ...726..108T}, which is very unlikely as it would mean that
\tol\ is at the center of a super rich cluster of galaxies,
contradicting observational evidence.
The remaining possibility is that \tol\ hosts a supermassive black hole of
$\sim 5\times 10^{9}$ M$_{\odot}$, corresponding to $10$ times its
estimated stellar and gaseous mass.

>>>>

Are these values atypical? If \tol\ followed the fundamental
plane relationship between its mean surface brightness
$I_e$, the projected half-light radius $R_e$ and the velocity dispersion
$\sigma$, described by $\log I_e=1.6 \log\sigma - 1.21\log R_e +
0.55$ \cite{2009ApJ...698.1590G},  the expected velocity dispersion
should be on the order of $5 \pm 1$ 
\kms, which is a factor of $\sim$ $12$ - $60$ lower than the 
results from the multiphase and rotation models, respectively. 
These are equivalent to factors of $\sim$ $140$ - $3600$ on the
dynamical mass;
\tol\ seems to be significantly more massive than the expectation from
scaling relationships for dwarf ellipticals.
A factor of $100$ in dynamical mass could be accounted by dark matter if
\tol\ was hosted by a dark matter halo of  $\sim 10^{16}$ M$_{\odot}$
\cite{2011ApJ...726..108T}, which is very unlikely as it would mean that
\tol\ is at the center of a super rich cluster of galaxies,
contradicting observational evidence.
The remaining possibility is that \tol\ hosts a supermassive black hole of
$\sim 5\times 10^{9}$ M$_{\odot}$, corresponding to $10$ times its
estimated stellar and gaseous mass.
